Evaluating Informative Hypotheses With Equality and Inequality Constraint: The Bayes Factor Encompassing Prior Approach

### 2021-09-19 Documents/Bookdown/01-case-study.Rmd
fix zero inflatiion and anova analyses

In this chapter, first, we describe the sample included in the study. Subsequently, we present the results of the cluster analysis to classify the different attachment patterns.

@@

### Externalizing Problems

@@

Externalizing problems according to attachment styles are reported in Table~\@ref(tab:table-cluster-ext).

@@

### Internalizing Problems

@@

Internalizing problems according to attachment styles are reported in Table~\ref(tab:table-cluster-ext).

>>>>

In this chapter, we describe the sample included in the study. First we present general information about the sample. Subsequently, we present the results of the cluster analysis to classify the different attachment patterns. Finally, we consider children's social-emotional problems.

@@

### Externalizing Problems {-}

@@

Overall, externalizing problems are low. This is expected as the sample is not a clinical sample. Externalizing problems according to attachment styles are reported in Table~\@ref(tab:table-cluster-ext).

@@

### Internalizing Problems {-}

@@

Overall, internalizing problems are low. Again, this is expected as the sample is not a clinical sample. Internalizing problems according to attachment styles are reported in Table~\ref(tab:table-cluster-ext).

### 2021-09-19 Documents/Bookdown/02-ext.Rmd
fix zero inflatiion and anova analyses

# Externalizing Problems {#ext}

blah blaah

[@guApproximatedAdjustedFractional2018]

>>>>

---
output: html_document
editor_options: 
  chunk_output_type: console
---
# Externalizing Problems {#ext}

In this chapter, we present the analyses to evaluate the different role of mother attachment and father attachment on children's externalizing problems. First, we discuss the appropriate models family to to take into account data characteristics. Next we conduct inference following three different approaches: 1) traditional Null Hypothesis Significance Testing (NHST) 2) Model Comparison using the AIC and BIC criteria 3) Bayes Factor with encompassing prior approach.

## Models Family Choiche

Externalizing problems are computed as the sum of 10 items of the SDQ, obtaining discrete scores that range from 0 to 20. Thus, we should use appropriate discrete distribution such as the *Poisson* distribution or the *Negative Binomial*. In the Poisson distribution mean and variance are defined according to the same parameter $\lambda$. On the contrary, Negative Binomial has an extra parameter to adjust the variance allowing more flexibility. Considering data distribution (see Figure~\@ref(fig:plot-externalizing-dist)), we can observe that data have high dispersion with a long right tail. In this case, Poisson distribution would be a poor choice and we prefer Negative Binomial instead.

Again, considering data distribution (see Figure~\@ref(fig:plot-externalizing-dist)), we can observe an high peak of values at zero. Remember that this is not a clinical sample, thus it is expected that children majority has no problems or really few problem. We could question ourselves, however, whether a *Zero-Inflated* model may be appropriate

### Zero Inflated Negative Binomial

To evaluate the presence of zero inflation in our data, we compare the number of observed zeros and expected zeros in a Negative Binomial mixed effects model. We consider in the model the role of gender and the interaction between mother attachment and father attachment. Moreover, we consider the children's classroom ID as a random effect to account for teachers' different ability to evaluate children's problems. Using R formula syntax, we have
```{r echo = TRUE, eval=FALSE}
# model formula
externalizing_sum ~ gender + mother * father + (1|ID_class)
```

The model is fitted using the function `glmmTMB()` from the `glmmTMB` R-package [@brooksGlmmTMBBalancesSpeed2017]. Next, we compare the number of observed zero and expected zeros using an adapted version the function `check_zeroinflation()` from the R-package `performance` [@ludeckePerformancePackageAssessment2021] that solves a small bug (see issue https://github.com/easystats/performance/issues/367).
```{r echo = TRUE, cache=TRUE}
my_check_zeroinflation(fit_ext_nb)
```

Results indicate that the model is slightly under-fitting the number of zeros. Now, we can try to fit a *Zero Inflated Negative Binomial* (ZINB) model and compare the performance of the two models. ZINB models are defined as
$$
y_{i} \sim ZINB(p_{i}, \mu_{i}, \phi),
$$
where $p_i$ is the probability of an observation $y_{i}$ being an extra zero (i.e., a zero not coming from the Negative Binomial distribution) and $1-p_i$ indicates the probability of a given observation $y_{i}$ being generated form a Negative Binomial distribution with mean $\mu_{i}$ and variance $\sigma_{i}^2 = \mu_{i} + \frac{\mu_{i}^2}{\phi}$. Moreover, we have that
$$
p_{i} = \text{logit}^{-1}(X_i^T\beta_p),\\
\mu_{i} = \text{exp}(X_i^T\beta_{\mu}).
$$
That is, both $p$ and $\mu$ are modelled separately according to (possibly) different variables. In our case, we consider only the role of gender for $p$ (i.e., the probability of having externalizing problems depends on gender), whereas for $\mu$ the consider also the interaction between mother attachment and father attachment. In both cases, we consider the children's classroom ID as a random effect (teachers may differ in they ability to detect children's problem and quantify them). Using R formula syntax, we have
```{r echo = TRUE, eval=FALSE}
# formula for p
p ~ gender + (1|ID_class)

# formula for mu
mu ~ gender + mother * father + (1|ID_class)
```

The ZINB model is fitted using the function `zeroinfl()` from the `pscl` R-package [@zeileisRegressionModelsCount2008]. To compare the ZINB model and the Negative Binomial model we conduct an analysis of *Deviance*. Note that, in the case of generalized linear models (GLM), the deviance is the corresponding of the residual variance used in the traditional ANOVA in the case of linear models.
```{r echo=TRUE, cache=TRUE}
anova(fit_ext_nb, fit_ext_zinb)
```

Overall, results indicate that the ZINB model performs better than the Negative Binomial model. Thus, in the following analyses we decide to use ZINB models.

## NHST

Following traditional NHST approach, we consider the model previously defind that includes all possible effects of interest. That is the gender effect and the interaction between mother attachment and father attachment. Subsequently, we can run an analysis of deviance to evaluate the significance of the predictors using the function `Anova()` from the R-package `car` [@foxCompanionAppliedRegression2019].
```{r, echo =TRUE, cache=TRUE}
car::Anova(fit_ext_zinb)
```
Results indicate a statistically significant effect of gender and mother attachment. On the contrary, the interaction and father attachment are no significant. Model summary is reported below.
```{r, echo =TRUE, cache=TRUE}
summary(fit_ext_zinb)
```
To evaluate the effect of gender and mother attachment, the marginal predicted values according to gender and mother attachment are presented separately in Figure~\@ref(fig:plot-nhst-effects). Not that the marginal predicted values for gender are averaged over mother and father attachment effects. Whereas, the marginal predicted values for mother attachment are averaged over father attachment and gender effect.
```{r plot-nhst-effects, fig.asp=.65, message=FALSE, fig.cap="Marginal predicted values according to gender and mother attachment. Values are averaged over the other effects ($n_{subj} = 847$)."}
get_plot_zinb(model = fit_ext_zinb, attachment = "mother")
```
